---
title: "Change of Evidence Vignette"
output: 
  html_document:
    keep_md: true
    self_contained: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

### Generate Sample Data

```{r}
set.seed(9878)

exp=rbinom(100,20,0.52)
con=rbinom(100,20,0.5)

summary(exp)
summary(con)

df <- data.frame(condition = c(rep("exp", 100), rep("con", 100)),
                      value = c(exp, con))
```

### Load library

```{r}
library(changeofevidence)
```

### Plot Random Walk
```{r}
rw_20bits <- cumsum(con - 10)  # Subtract chance level (10)
plotrw(rw_20bits, n_bits = 20)
```

## Sequential Bayesian Analysis of t-tests
### Calculate Sequential Bayes Factors

```{r}
# Undirectional one-sample t-tests with broad prior
bf.exp <- bfttest(exp, mu = 10, alternative = "two.sided", prior.loc = 0, prior.r = 0.707)
print(bf.exp)

# Use exact=FALSE for a quicker test that doers not calculate every single BF
bf.con <- bfttest(con, mu = 10, alternative = "two.sided", prior.loc = 0, prior.r = 0.707, exact=FALSE)
print(bf.con)

# only the last 5 data points
bfttest(con, mu = 10, alternative = "two.sided", prior.loc = 0, prior.r = 0.707, nstart = length(con)-5)

# Directional paired samples t-test with narrow prior
bf.paired <- bfttest(exp, con, alternative = "greater", prior.loc = 0, prior.r = 0.1)
print(bf.paired)

# Independent samples t-test with informed prior
bf.between <- bfttest(value ~ condition, data = df, alternative = "less", prior.loc = 0.1, prior.r = 0.1)
print(bf.between)

```

### Non-parametric Sequential Bayes Factors
```{r}
# One-sample Wilcoxon signed-rank test
bf.onesample.np <- bfttest(exp, mu = 10, alternative = "two.sided", prior.loc = 0, prior.r = 0.707, exact = FALSE, parametric = FALSE)
print(bf.onesample.np)

# Paired Wilcoxon signed-rank test
bf.paired.np <- bfttest(exp, con, alternative = "greater", prior.loc = 0, prior.r = 0.1, exact = FALSE, parametric = FALSE)
print(bf.paired.np)

# Mann-Whitney U test
bf.between.np <- bfttest(value ~ condition, data = df, alternative = "less", prior.loc = 0.1, prior.r = 0.1, exact = FALSE, parametric = FALSE)
print(bf.between.np)
```

### Plot Seq BFs

```{r}
# Plot seqbf object
plot(bf.paired)

# Plot multiple BFs
plotbf(list(exp=bf.exp$BF, con=bf.con$BF))
```

### Robustness analyis

```{r}
bf.paired.robust <- bfRobustness(bf.paired)
print(bf.paired.robust)
plot(bf.paired.robust)
```

## Additional Sequential Tests
### Bayesian Sequential Binomial Test
```{r}
data <- rbinom(100, 1, 0.6)
bf.binom <- bfbinom(data, p = 0.5, alternative = "greater")
print(bf.binom)
plot(bf.binom)
```

### Bayesian Sequential Correlation Test
```{r}
x <- rnorm(100)
y <- x + rnorm(100, 0, 5)  # Correlated data
bf.cor <- bfcor(x, y, alternative = "greater")
print(bf.cor)
plot(bf.cor)
```

## Simulations
### Create simulations as empirical null distribution

```{r results='hide'}
# Indicate the amount of trials of one experimental run (e.g. 100 subjects * 20 trials)
# Specify the same test parameters as the test(s) you want to compare to (in this case the one-sample t-tests.)
sims <- simcreate(100*20, n.sims = 100, mean.scores = 10, use.files = F, alternative = "two.sided", prior.loc = 0, prior.r = 0.707)
```

### Plot BFs with simulation data

```{r}
plot(bf.paired, sims.df = sims)
plotbf(list(exp=bf.exp$BF, con=bf.con$BF), sims.df = sims)
```

## Change of Evidence Measures
### Calculate All Change of Evidence (CoE) Measures
```{r}
coe <- coe(bf.exp, sims)
print(coe)
plot(coe)
```

### Individual Change Of Evidence Measures

```{r}
# Max BF
r.exp.maxbf <- maxbf(bf.exp, sims.df = sims)
r.con.maxbf <- maxbf(bf.con, sims.df = sims)

# Energy BF
r.exp.nrg <- energybf(bf.exp, sims.df = sims)
r.con.nrg <- energybf(bf.con, sims.df = sims)

# FFT Amplitude Sum
fft.exp <- fftcreate(bf.exp)
fft.con <- fftcreate(bf.con)

r.exp.fft <- ffttest(fft.exp, sims.df = sims)
r.con.fft <- ffttest(fft.con, sims.df = sims)

plotfft(fft.exp, sims.df = sims)
```
